\documentclass{article}

\usepackage{pvs} % problems in pvs: uses amsopn,
                 % which defines conflicting theorem/lemma etc
\usepackage{latexsym}
\usepackage{amsopn}
\usepackage{amsfonts}
\usepackage{alltt}

\begin{document}

\section{Introduction}

This set of libraries defines the extended nonnegative reals ({\it
  i.e} the nonnegative reals with $\infty$) as a boolean/nonnegative
real tuple. If one can get past the cluttered notation ({\it e.g.}
\pvsid{x\_eq} for $=$), it actually works quite well in practice.

The primary purpose of this library is to support measure theory, so
the operations supported are quite restricted. Notice that there is no
\pvsid{x\_ge}, \pvsid{x\_gt} defined. However, we {\em are} interested
in sums and limits, including least upper bounds and greatest lower
bounds.

There are three supporting libraries, which may be of more general
interest. The first is \pvsid{code\_product}, which performs a
diagonal traversal of a doubly indexed sequence. A nice way to use
this feature is shown in \pvsid{double\_index}, where the deft use of
\pvsid{double\_index} turns a sequence into a doubly-indexed function,
and \pvsid{single\_index} turns a doubly-indexed function back into a
sequence.

The final supporting library -- \pvsid{double\_nn\_sequence} allows us
to manipulate double sums. It relies (obviously) on the items being
manipulated being non-negative. Put simply, one needs to pay a great
deal of attention to re-ordering infinite sums if the series are not
absolutely convergent. If someone wants to put in the work to
generalize this result to more general series, feel free. I'd suggest
using the result for non-negative sums as a starting point.

\appendix
\newpage
\section{Library extended\_nnreal}
\input{extended_nnreal.tex}
\newpage
\section{Library code\_product}
\input{code_product.tex}
\newpage
\section{Library double\_index}
\input{double_index.tex}
\newpage
\section{Library double\_nn\_sequence}
\input{double_nn_sequence.tex}

\end{document}